% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]

\documentclass[9pt]{beamer}
\usetheme{Madrid}
\usecolortheme{beaver}
\usepackage{amsmath,amssymb,amsthm,asymptote,graphicx}
\usepackage{graphics}
% \usepackage{bisvslides}
\usepackage{arcs}
\graphicspath{{./images}}

\newcounter{problem}[section]

\title{Mixed Practice}
\subtitle{Mathcounts 21 - Session 6}
\author{Derrick L., Krihnaveni P., Irene W.}
\institute{BISV Mathcounts Club 21}
\date{January 25, 2022}

\begin{document}

% Generate title page
\begin{frame}
    \titlepage        
\end{frame}
% \setbeamertemplate{footline}[miniframes Madrid]

\section{Beginner Problems}
\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2021 School, Team \#2]
    A container is one-half full. After 20 ounces are poured out, the container is one-third full. How many ounces are still in the container?
    
    
    \end{block}
\end{frame}



\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2021 School, Team \#10]
    What is the remainder when $2021^{2021}$ is divided by 7?
    
    
    \end{block}
\end{frame}


% Difficulty: 4 • Answer: 1/4
\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts]
    Four packages are delivered to four houses, one to each house. If these packages are randomly delivered, what is the probability that exactly two of them are delivered to the correct houses? Express your answer as a common fraction.
	
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts Handbook 2020-21, \#236]
     How many subsets of one or more elements of the set {1, 2, 3, 4, 5, 6, 7, 8, 9, 10} contain the element 1 or the element 2 or both?
     
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts]
    % Concept: Geometry • Difficulty: 4 • Answer: 50 • Solution Available: Yes (Hide) • Report an error with this problem.

 Right $\triangle ABC$ with legs $AB=3$ cm and $CB=4$ cm is rotated about one of its legs. What is the greatest possible number of cubic centimeters in the volume of the resulting solid? Express your answer to the nearest whole number.
	
    \end{block}
\end{frame}


\section{Intermediate Problems}
\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[2018 Purple Comet, HS \#2]
    A triangle with side lengths $16$, $18$, and $21$ has a circle with radius $6$ centered at each vertex. Find $n$ so that the total area inside the three circles but outside of the triangle is $n\pi$.

    
    \end{block}

    \begin{center}
        \begin{asy}
            pair A, B, C;
            path w1, w2, w3;
    
            unitsize (0.2 cm);
            B = (0, 0);
            C = (21, 0);
            A = intersectionpoint (circle (B, 16), circle (C, 18));
    
            w1 = circle (A, 6);
            w2 = circle (B, 6);
            w3 = circle (C, 6);
    
            fill(buildcycle(w1, B--A, C--A),gray (0.85));
            fill(buildcycle(reverse(w2), A--B, C--B),gray (0.85));
            fill(buildcycle(reverse(w3), B--C, C--A),gray (0.85));
    
            draw (A--B--C--A);
            draw (w1^^w2^^w3);
    
        \end{asy}
    \end{center}

\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2017 State, Sprint \#19]
A pole of radius 1 inch and height $h$ inches is perpendicular to the ground. A
snake is coiled around the pole in a spiral pattern, making a 60-degree angle
with the ground. If the snake is $9\pi$ inches long and reaches from the ground to the top of the pole, then $h$ can be written in the form $a \pi \sqrt{b}$, where $a$ is a rational
number and $b$ is a positive integer that is not divisible by the square of any
prime. What is the value of $a + b?$ Express your answer as a common fraction.
    
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[2017 Mathcounts National, Sprint \#9]
    Matt left home traveling towards the mountains to go camping. His brother Mark started along the same route 2.1 hours later traveling at a rate 35 mi/h faster trying to catch up to Matt. What was Matt's average speed if it took Mark 1.2 hours to catch up to him.
    
    
    \end{block}
\end{frame}

\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2017 State, Sprint \#29]
Lines $AB$ and $DC$ are parallel, and transversals $AC$ and $BD$ intersect at a point $X$ between the two lines so that $\frac{AX}{CX} = \frac{5}{7}.$ Points $P$ and $Q$ lie on segments $AB$ and $DC$, respectively. The segment $PQ$ intersects transversals $BD$ and $AC$ at points $M$ and $N,$ respectively, so that $PM = MN = NQ.$ What is the ratio $\frac{AP}{BP}?$ Express your answer as a common fraction.	
    
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2015 State Target \#6]
The shape below can be folded along the dashed lines and taped together along
the edges to form a three-dimensional polyhedron. All lengths in the diagram are
given in inches. What is the volume of the resulting polyhedron? Express your
answer in simplest radical form.

    
    \end{block}
    \begin{center}
        \begin{asy}
            import olympiad;
            unitsize (0.35cm);
    
            pair A, B, C, D, E, F, G, H, I, J;
    
            A = (0, 0);
            B = (4, 0);
            C = (4, 7);
            D = (0, 7);
            E = (-4, 0);
            F = (-4, 4);
            G = (8, 0);
            H = (8, 4);
            I = rotate (-60, A) * B;
            J = (2, 7 + sqrt(21));
    
            draw (A--B, L="4", dashed);
            draw (D--A, L="7", dashed);
            draw (B--C, L="7", dashed);
            draw (C--D, L="4", dashed);
            draw (A--I, L="4");
            draw (I--B, L="4");
            draw (B--G, L="4");
            draw (G--H, L="4");
            draw (H--C, L="5");
            draw (C--J, L="5");
            draw (E--A, L="4");
            draw (F--E, L="4");
            draw (D--F, L="5");
            draw (J--D, L="5");
            draw (rightanglemark (D, A, E, 10));
            draw (rightanglemark (A, E, F, 10));
            draw (rightanglemark (G, B, C, 10));
            draw (rightanglemark (H, G, B, 10));
        \end{asy}
    \end{center}
    
\end{frame}


% Other Geometry
\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2015 State Team \#3]
    Equilateral triangle $ABC$ with side-length 12 cm is inscribed in a circle. What is the area of the largest equilateral triangle that can be drawn with two vertices on segment $AB$ and the third vertex on minor arc $AB$ of the circle? Express your answer in simplest radical form.
    
    
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2018 National, Sprint \#6]
    If the three lines $ 3x+y=-1,x+3y=-11 $ and $ ax-2y=3 $ all intersect at one point, what is the value of $ a $?
    
    \end{block}
\end{frame}

%--------------
\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2018 National, Sprint \#9]
    The mean, median and unique mode of a list of seven positive integers are all equal to 10. What is the greatest possible range of the list?
    
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2018 National, Sprint \#13]
    What common fraction is equivalent to the sum shown?
    \[ \frac{1}{2018+1} + \frac{1}{2018^2+2018+1} + \frac{1}{2018^4+2(2018^3)+2(2018^2)+2018} \]
    
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2018 National, Sprint \#21]
    What is the greatest integer that is less than or equal to $ \dfrac{3^{19} + 2^{19}}{3^{15} + 2^{15}} $?
    
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2018 National, Sprint \#23]
    Xena and Yolanda toss an unfair coin that lands heads up $ 75\% $ of the time. If the coin lands heads up, Xena gets a point. Otherwise, Yolanda gets a point. The game ends when one player has a two-point lead over the other, and the player with the two-point lead is the winner. What is the probability that Xena wins the game? Express your answer as a common fraction.
    
    \end{block}
\end{frame}

%--------------

\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts 2018 National, Sprint \#24]
    The figure shows isosceles right triangle $ ABC $ with $ AC=BC=16 $ units. Triangle $ ABD $ is constructed within triangle $ ABC $ with vertex $ D $ on side $ AC $ and $ AD = 4 $ units. Point $ E $ is drawn on side $ AB $ to form isosceles right triangle $ ADE $. A series of isosceles right triangles is constructed within triangle $ ABD $, such that the hypotenuse of each lies on side $ AB $, the 90-degree vertex of each lies on segment $ BD $, and each shares a vertex with the preceding triangle in the series, as shown. What is the combined area of the series of isosceles right triangles within triangle $ ABD $? Express your answer as a common fraction.    

    
    \end{block}
    \begin{center}
        \begin{asy}
            import olympiad;

            unitsize(0.35cm);
            pair A, B, C, D, E, F, G, H, I, J, K, L;

            A = (0,0);
            B = (16, 0);
            C = (8, 8);
            D = (2, 2);
            E = (4, 0);

            F = (E.x+(3/4)*2, (3/4)*2);
            G = (E.x+(3/4)*4, 0);

            H = (G.x+(3/4)*(3/4)*2, (3/4)*(3/4)*2);
            I = (G.x+(3/4)*(3/4)*4, 0);

            J = (I.x+(3/4)*(3/4)*(3/4)*2, (3/4)*(3/4)*(3/4)*2);
            K = (I.x+(3/4)*(3/4)*(3/4)*4, 0);

            L = (K.x+(3/4)*(3/4)*(3/4)*(3/4)*2, (3/4)*(3/4)*(3/4)*(3/4)*2);

            draw(A--B--C--cycle);
            draw(B--D--E--F--G--H--I--J--K--L);

            draw(rightanglemark(A, C, B));
            draw(rightanglemark(A, D, E));
            draw(rightanglemark(E, F, G));
            draw(rightanglemark(G, H, I));
            draw(rightanglemark(I, J, K));

            label("$A$", A, SW);
            label("$B$", B, SE);
            label("$C$", C, N);
            label("$D$", D, NW);
            label("$E$", E, S);
            label("$F$", F, N);
            label("$G$", G, S);
            label("$16$", B--C, NE);
            label("$4$", A--D, NW);

            label("$\ldots$", (L.x+0.4, L.y/2));
        \end{asy}
    \end{center}

\end{frame}


%-------------------------------------------------------
\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Mathcounts]
A circle is tangent to the positive $ x- $axis at $ x = 3 $. It passes through the distinct points $ (6, 6) $ and $ (p, p) $ where $ p $ is not 6. What is the value of $ p $? Express your answer as a common fraction.
	
    \end{block}
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[2009 Purple Comet, HS \#7]
    The figure $ABCD$ is bounded by a semicircle $CDA$ and a quarter circle $ABC$. Given that the distance from $A$ to $C$ is $18$, find the area of the figure.

    
    \end{block}
    \begin{center}
        \begin{asy}
        import cse5;
        import olympiad;
    size(100);
    defaultpen(linewidth(0.8));
    pair A=(-9,0),B=(0,9*sqrt(2)-9),C=(9,0),D=(0,9);
    dot(A^^B^^C^^D);
    draw(arc(origin,9,0,180)^^arc((0,-9),9*sqrt(2),45,135));
    label("$A$",A,S);
    label("$B$",B,N);
    label("$C$",C,S);
    label("$D$",D,N);
        
        \end{asy}
    \end{center}
    
    
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[Purple Comet]
    Three lines are drawn parallel to each of the sides of triangle $ABC$
so that they intersect in the interior of $ \triangle ABC $. The resulting three smaller triangles have areas 1, 4, and 9. Find the area of triangle $ABC$. 
	
    \end{block}

    \begin{center}
        \begin{asy}
        import cse5;
        unitsize(0.6cm);
        
        pair A, B, C, D, E, F, G, H, I, J;
        real r1 = 1/2, r2 = 2/3;
        
        A = (0,0);
        B = (5,0);
        C = (3,7);
    
        E = (1/6)*(A + B);
        F = (4/6)*(A + B);
        
        G = (1/2)*(A + C);
        H = A + (2/3)*(C - A);
        
        I = (1/2)*(B + C);
        J = B + (5/6)*(C - B);
        
        D = G + (1/3)*(I - G);
        draw(A--B--C--A^^E--J^^F--H^^G--I);
        
        label("$A$", A, S);
        label("$B$", B, S);
        label("$C$", C, N);
        
        label("1", (D + G + H) / 3);
        label("4", (D + I + J) / 3);
        label("9", (D + E + F) / 3);
        
        
        \end{asy}
    \end{center}
    
\end{frame}


\refstepcounter{problem}
\begin{frame}[t, fragile]{Problem \thesection.\theproblem}
    \begin{block}{}[2017 AMC 12]
    An ice-cream novelty item consists of a cup in the shape of a 4-inch-tall frustum of a right circular cone, with a 2-inch-diameter base at the bottom and a 4-inch-diameter base at the top, packed solid with ice cream, together with a solid cone of ice cream of height 4 inches, whose base, at the bottom, is the top base of the frustum. What is the total volume of the ice cream, in cubic inches? Express your answer in terms of $\pi$.
	
    \end{block}
\end{frame}


\newpage



\end{document}