% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]

\documentclass[9pt]{beamer}
\usetheme{Madrid}
\usecolortheme{beaver}
\usepackage{amsmath,amssymb,amsthm,asymptote,graphicx}
\usepackage{graphics}
% \usepackage{bisvslides}

\title{Number Sense}
\subtitle{Mathcounts 20 - Session 4}
\author{bisv.math@gmail.com}
\institute{BISV Mathcounts Club 20}
\date{December 15, 2020}

%\maketitle
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Informations
%\title{TEMPLATE}

%\titlegraphic{assets/gkg.png} %change this to your preferred logo or image(the image is located on the top right corner).
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\begin{document}

% Generate title page
\titlepage

% \begin{frame}

%  \frametitle{TABLE OF CONTENTS}
%  \tableofcontents
% \end{frame}


\section{Beginner Problems}
\begin{frame}
    \begin{alertblock}{}
        \begin{flushright}
        {\huge Beginner Problems}
        \end{flushright}
    \end{alertblock}
\end{frame}

\begin{frame}[t]{7.1}
    \begin{block}{}
        Danica wants to arrange her model cars in rows with exactly
        6 cars in each row. She now has 23 model cars. What is the
        smallest number of additional cars she must buy in order to
        be able to arrange her cars in this way?
        
    \end{block}
    \end{frame}
    
    % Difficulty: 1 • Answer: 31 zeros
    \begin{frame}[t]{7.2}
    \begin{block}{}
         How many zeros are after the last nonzero digit of $125!$? \textit{(Mathcounts)}
        
    \end{block}
    \end{frame}
    
    % Topic: Multiples • Difficulty: 3 • Answer: 1197 
    \begin{frame}[t]{7.3}
    \begin{block}{}
        What number is less than $35^2$, greater than $34^2$, divisible by 19, and a multiple of 9? \textit{(Mathcounts)}
         
    \end{block}
    \end{frame}
    
    % Topic: Exponentiation • Difficulty: 5 • Answer: 86 
        
    \begin{frame}[t]{7.4}
    \begin{block}{}
        What is the value of $ \dfrac{4^{26}+8^{15}}{32^{9} + 16^{11}} $ ? \textit{(Mathcounts Handbook 2020-21, \#205)}
         
    \end{block}
    \end{frame}
    
    % Topic: Multiples • Difficulty: 3 • Answer: 1197 
    \begin{frame}[t]{7.5}
    \begin{block}{}
        What is the greatest two-digit prime number that is one greater than a perfect square? \textit{(Mathcounts Handbook 2020-21, \#60)}
         
    \end{block}
    \end{frame}
    
    % Topic: Legendre • Difficulty: 4 • Answer: 23
    \begin{frame}[t]{7.6}
    \begin{block}{}
        In how many consecutive zeroes does the product $115 \times 116 \times 117 \ldots \times 201$ end? \textit{(Mathcounts)}
         
    \end{block}
    \end{frame}
    
     
    
     
    
    % Topic: Modular Arithmetic, Difficulty: 4, Answer: 2
    \begin{frame}[t]{7.7}
    \begin{block}{}
        What is the remainder when $5981 \times 8162 \times 476$ is divided by 5? \textit{(Mathcounts Handbook 2015-16)}
         
    \end{block}
    \end{frame}
    
    \begin{frame}[t]{7.8}
    \begin{block}{}
        \textit{(Mathcounts)} Friends Megan and Heather go to different schools.  Megan has math class during first period on each of the 180 days she goes to school.  She will be in math class a total of 8640 minutes this year.  Heather’s school year also has 180 days, but her math class only meets every other day, so her class periods are longer.  (One day she’ll have math class, and then the next day she won’t.)  If Megan and Heather end up with the same number of minutes of math class each year, how long are the class periods at Heather’s school?
        
    \end{block}
    \end{frame}
    

\section{Intermediate Problems}
\begin{frame}
    \begin{alertblock}{}
        \begin{flushright}
        {\huge Intermediate Problems}
        \end{flushright}
    \end{alertblock}
\end{frame}

\begin{frame}[t]{8.1}
    \begin{block}{}
        \textit{(Alcumus)} Suppose $a$ and $b$ are positive integers, neither of which is a multiple of 3. Find the least possible remainder when $a^2 + b^2$ is divided by 3.
        
    \end{block}
    \end{frame}
    
    % Concept: Recurrence • Difficulty: 3 • Answer: 76 1s 
    
     
     \begin{frame}[t]{8.2}
    \begin{block}{}
        Becky tries an experiment. She writes some numbers on the blackboard and then applies the following rule: she picks any number on the board that is greater than $1$, erases it and replaces it with the list of its proper divisors. For example, if the number $6$ was on the board, she would apply the rule by erasing the $6$ and replacing it with the numbers $1$, $2$ and $3.$ The experiment ends when there are only $1$s left on the board. If Becky begins with just the number $72$ on the board, how many $1$s will be on the board when she is finished? \textit{(Mathcounts Handbook, 2014-15)}
        
    \end{block}
    \end{frame}
    % Difficulty: 4 • Answer: 16 
    \begin{frame}[t]{8.3}
    \begin{block}{}
        After Carlos accidentally spills water on his paper, he is left with the partial equation $1729^2 - 2 \times 1730^2 + 17\Box\Box^2 = 34\Box\Box,$ where each $\Box$ represents a smudged digit, not necessarily all the same. What is the sum of the four smudged digits? \textit{You may use calculator for this question.} \textit{Mathcounts Handbook, 2012-13}
        
    \end{block}
    \end{frame}
     
    %  Concept: Number Theory • Difficulty: 5 • Answer: 45 • 
    \begin{frame}[t]{8.4}
    \begin{block}{}
        The smallest case of 5 consecutive odd integers whose sum is a perfect square is 1, 3, 5, 7, 9. (1+3+5+7+9 = 25.) Find the median of the next larger set of 5 consecutive odd integers whose sum is a perfect square.
        
    \end{block}
    \end{frame}
    
    \begin{frame}[t]{8.5}
    \begin{block}{}
        \textit{(MathCounts)} Kevin and Devin each makes one hat per day for charity, but they started on different days. Today, Kevin made his 520th hat, and Devin made his 50th. A celebration is planned for the next date that Kevin’s hat count is evenly divisible by Devin’s hat count. In how many days from today will they celebrate?
        
    \end{block}
    \end{frame}
    
    
    \begin{frame}[t]{8.6}
    \begin{block}{}
        If $523_b = 262$, what is the value of $b$? \textit{(MathCounts)} 
        
    \end{block}
    \end{frame}
    
    % Topic: Modular Arithmetic, Answer: 1
    \begin{frame}[t]{8.7}
    \begin{block}{}
        Find the remainder when $4^{18}\cdot19^{80}$ is divided by 9. \textit{(AoPS Introduction to Number Theory)} 
        
    \end{block}
    \end{frame}
    
    % Topic: Modular Arithmetic, Difficulty: 6, Answer: 59
    \begin{frame}[t]{8.8}
    \begin{block}{}
        When organizing her pens, Faith notices that when she puts them in groups of 3, 4, 5, or 6, she is always one pen short of being able to make full groups. If Faith has between 10 and 100 pens, how many pens does she have? \textit{(Mathcounts Handbook 2015-16)}
         
    \end{block}
    \end{frame}
    
    \begin{frame}[t]{8.9}
    \begin{block}{}
        \textit{(AMC 10)} How many base-10 three-digit numbers are also three-digit numbers in both base-9 and base-11?
        
    \end{block}
    \end{frame}
    
    \begin{frame}[t]{8.10}
    \begin{block}{}
        Chicken McNuggets can be purchased in quantities of 6, 9, and 20 pieces. You can buy exactly 15 pieces by purchasing a 6 and a 9, but you can’t buy exactly 10 McNuggets. What is the largest number of McNuggets that can NOT be purchased?
        
    \end{block}
    \end{frame}
    
%----------------------------
\newpage
\section{Challenge Problems}
\begin{frame}
    \begin{alertblock}{}
        \begin{flushright}
        {\huge Challenge Problems}
        \end{flushright}
    \end{alertblock}
\end{frame}

\begin{frame}[t]{9.1}
\begin{block}{}
   \textit{(MathCounts)}  To weigh an object by using a balance scale, Brady places the object on one side of the scale and places enough weights on each side to make the two sides of the scale balanced. Brady’s set of weights contains the minimum number necessary to measure the whole-number weight of any object from 1 to 40 pounds, inclusive. What is the greatest weight, in pounds, of a weight in Brady’s set?
	
\end{block}
\end{frame}

\begin{frame}[t]{9.2}
\begin{block}{}
   \textit{(Pascal 2013, \#24)}  Pascal High School organized three different trips. Fifty percent of the students went on the first trip, 80\% went on the second trip, and 90\% went on the third trip. A total of 160 students went on all three trips, and all of the other students went on exactly two trips. How many students are at Pascal High School?

	
\end{block}
\end{frame}


\begin{frame}[t]{9.3}
\begin{block}{}
    In the United States, coins have the following thicknesses: penny, $1.55$ mm; nickel, $1.95$ mm; dime, $1.35$ mm; quarter, $1.75$ mm. If a stack of these coins is exactly $14$ mm high, how many coins are in the stack? \textit{(2004 AMC 10, \#13)}

       
\end{block}
\end{frame}
\newpage

\end{document}
